Long-form recording of infant body position in the home using wearable inertial sensors

### 2023-03-24 manuscript.Rmd
Updated reliability

A primary coder completed annotation for the full length of the video, while an independent reliability coder completed annotation for the first thirty minutes of each video. Interrater reliability was based on the proportion of video frames that the two coders chose the same body position code. Overall agreement averaged 90.5% across video files, ranging from 68.4%-100%. Cohen's *kappa* averaged 85.5% across video files, ranging from 31.0%-100%.
<!-- UPDATE THESE BEFORE SUBMITTING -->

@@

Overall accuracy (Figure \@ref(fig:metrics)A) represents the proportion of 4-s windows in the testing set in which the model prediction matched the human annotation of body position. Overall accuracy for group models  (*M* = `r metrics_lookup["Overall Accuracy", "mean_Group"]`) was slightly lower than accuracy for individual models (*M* = `r metrics_lookup["Overall Accuracy", "mean_Individual"]`). Although overall accuracy from our unsupervised, in-home data collection did not match the near-perfect accuracy  (.95-.98) found in prior in-lab studies [@FranchakScott2021; @AiraksinenRasanen2020], both models approached the level of agreement found between two human coders (*M* = .905). Most likely, lower accuracy in the current study results from the more variable and complex behavior observed in an unsupervised setting rather than from a difference in the quality of the classification model. Visual inspection of Figure \@ref(fig:metrics)A shows that accuracy values were heavily skewed, with most approaching perfect accuracy but a few participants with very poor accuracy. Looking at the median performance suggests that the difference between models was not as wide for the typical participant (group median accuracy = `r metrics_lookup["Overall Accuracy", "median_Group"]`; individual median accuracy = `r metrics_lookup["Overall Accuracy", "median_Individual"]`. Indeed, it is notable that the worst-case accuracy from group models (minimum = `r metrics_lookup["Overall Accuracy", "min_Group"]`) was considerably lower than in individual models (minimum = `r metrics_lookup["Overall Accuracy", "min_Individual"]`). Possibly, individual models accounted for idiosyncrasies in behavior or inconsistencies in sensor placement for those sessions that group models could not generalize to.

@@

agreement_scatter <- function(ds) {
  ggplot() +
  geom_point(data = filter(ds, file %in% outlier_files), mapping = aes(x = prop_human, y = prop_model, shape = file, fill = pos), fill = "#333333", size = 4, alpha = .5) + 
  geom_point(data = filter_outliers(ds), mapping = aes(x = prop_human, y = prop_model, fill = pos), shape = 21, alpha = .5, size = 4) + 
  geom_abline(intercept = 0, slope = 1) + 
  scale_fill_manual(values = pal, guide = "none") + 
  scale_shape_manual(guide = "none", values = 22:23) + 
  scale_x_continuous(breaks = c(0,.5,1), labels = c(0, 50, 100), limits = c(-.07, 1.07), name = "Actual Prevalence (%)") + 
  scale_y_continuous(breaks = c(0,.5,1), labels = c(0, 50, 100), limits = c(-.07, 1.07), name = "Predicted Prevalence (%)") + 
  facet_wrap("pos", ncol = 2, as.table = T) +
  theme(panel.spacing.x = unit(1, "lines")) +
  theme(panel.spacing.y = unit(1, "lines")) + 
  theme(strip.background = element_blank(), strip.text.x = element_text(size = 16, face = "bold"))
}

>>>>

A primary coder completed annotation for the full length of the video, while an independent reliability coder completed annotation for the first thirty minutes of each video. Interrater reliability was based on the proportion of video frames that the two coders chose the same body position code. Overall agreement averaged 90.9% across video files, ranging from 68.4%-100%. Cohen's *kappa* averaged 86.1% across video files, ranging from 31.0%-100%.

@@

Overall accuracy (Figure \@ref(fig:metrics)A) represents the proportion of 4-s windows in the testing set in which the model prediction matched the human annotation of body position. Overall accuracy for group models  (*M* = `r metrics_lookup["Overall Accuracy", "mean_Group"]`) was slightly lower than accuracy for individual models (*M* = `r metrics_lookup["Overall Accuracy", "mean_Individual"]`). Although overall accuracy from our unsupervised, in-home data collection did not match the near-perfect accuracy  (.95-.98) found in prior in-lab studies [@FranchakScott2021; @AiraksinenRasanen2020], both models approached the level of agreement found between two human coders (*M* = .906). Most likely, lower accuracy in the current study results from the more variable and complex behavior observed in an unsupervised setting rather than from a difference in the quality of the classification model. Visual inspection of Figure \@ref(fig:metrics)A shows that accuracy values were heavily skewed, with most approaching perfect accuracy but a few participants with very poor accuracy. Looking at the median performance suggests that the difference between models was not as wide for the typical participant (group median accuracy = `r metrics_lookup["Overall Accuracy", "median_Group"]`; individual median accuracy = `r metrics_lookup["Overall Accuracy", "median_Individual"]`. Indeed, it is notable that the worst-case accuracy from group models (minimum = `r metrics_lookup["Overall Accuracy", "min_Group"]`) was considerably lower than in individual models (minimum = `r metrics_lookup["Overall Accuracy", "min_Individual"]`). Possibly, individual models accounted for idiosyncrasies in behavior or inconsistencies in sensor placement for those sessions that group models could not generalize to.

@@

agreement_scatter <- function(ds) {
  ggplot() +
  geom_point(data = filter(ds, file %in% outlier_files), mapping = aes(x = prop_human, y = prop_model, shape = file, fill = pos), fill = "#333333", size = 4, alpha = .5) + 
  geom_point(data = filter_outliers(ds), mapping = aes(x = prop_human, y = prop_model, fill = pos), shape = 21, alpha = .5, size = 4) + 
  geom_abline(intercept = 0, slope = 1) + 
  scale_fill_manual(values = pal, guide = "none") + 
  scale_shape_manual(guide = "none", values = 22:23) + 
  scale_x_continuous(breaks = c(0,.5,1), labels = c(0, 50, 100), limits = c(-.07, 1.07), name = "Actual Time (%)") + 
  scale_y_continuous(breaks = c(0,.5,1), labels = c(0, 50, 100), limits = c(-.07, 1.07), name = "Predicted Time (%)") + 
  facet_wrap("pos", ncol = 2, as.table = T) +
  theme(panel.spacing.x = unit(1, "lines")) +
  theme(panel.spacing.y = unit(1, "lines")) + 
  theme(strip.background = element_blank(), strip.text.x = element_text(size = 16, face = "bold"))
}

### 2023-03-24 manuscript.tex
Updated reliability

A primary coder completed annotation for the full length of the video, while an independent reliability coder completed annotation for the first thirty minutes of each video. Interrater reliability was based on the proportion of video frames that the two coders chose the same body position code. Overall agreement averaged 90.5\% across video files, ranging from 68.4\%-100\%. Cohen's \emph{kappa} averaged 85.5\% across video files, ranging from 31.0\%-100\%.

@@

Overall accuracy (Figure \ref{fig:metrics}A) represents the proportion of 4-s windows in the testing set in which the model prediction matched the human annotation of body position. Overall accuracy for group models (\emph{M} = 0.85) was slightly lower than accuracy for individual models (\emph{M} = 0.92). Although overall accuracy from our unsupervised, in-home data collection did not match the near-perfect accuracy (.95-.98) found in prior in-lab studies (Airaksinen et al., 2020; Franchak et al., 2021), both models approached the level of agreement found between two human coders (\emph{M} = .905). Most likely, lower accuracy in the current study results from the more variable and complex behavior observed in an unsupervised setting rather than from a difference in the quality of the classification model. Visual inspection of Figure \ref{fig:metrics}A shows that accuracy values were heavily skewed, with most approaching perfect accuracy but a few participants with very poor accuracy. Looking at the median performance suggests that the difference between models was not as wide for the typical participant (group median accuracy = 0.89; individual median accuracy = 0.93. Indeed, it is notable that the worst-case accuracy from group models (minimum = 0.50) was considerably lower than in individual models (minimum = 0.73). Possibly, individual models accounted for idiosyncrasies in behavior or inconsistencies in sensor placement for those sessions that group models could not generalize to.

>>>>

A primary coder completed annotation for the full length of the video, while an independent reliability coder completed annotation for the first thirty minutes of each video. Interrater reliability was based on the proportion of video frames that the two coders chose the same body position code. Overall agreement averaged 90.9\% across video files, ranging from 68.4\%-100\%. Cohen's \emph{kappa} averaged 86.1\% across video files, ranging from 31.0\%-100\%.

@@

Overall accuracy (Figure \ref{fig:metrics}A) represents the proportion of 4-s windows in the testing set in which the model prediction matched the human annotation of body position. Overall accuracy for group models (\emph{M} = 0.85) was slightly lower than accuracy for individual models (\emph{M} = 0.92). Although overall accuracy from our unsupervised, in-home data collection did not match the near-perfect accuracy (.95-.98) found in prior in-lab studies (Airaksinen et al., 2020; Franchak et al., 2021), both models approached the level of agreement found between two human coders (\emph{M} = .906). Most likely, lower accuracy in the current study results from the more variable and complex behavior observed in an unsupervised setting rather than from a difference in the quality of the classification model. Visual inspection of Figure \ref{fig:metrics}A shows that accuracy values were heavily skewed, with most approaching perfect accuracy but a few participants with very poor accuracy. Looking at the median performance suggests that the difference between models was not as wide for the typical participant (group median accuracy = 0.89; individual median accuracy = 0.93. Indeed, it is notable that the worst-case accuracy from group models (minimum = 0.50) was considerably lower than in individual models (minimum = 0.73). Possibly, individual models accounted for idiosyncrasies in behavior or inconsistencies in sensor placement for those sessions that group models could not generalize to.
